---
title: ""
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    smooth_scroll: false
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(reshape2)
library(tidyverse)
library(rtracklayer)
library(isoband)
library(sf)
library(MASS)
library(lwgeom)
library(ggrepel)
library(hexbin)
library(ggrastr)
library(viridis)
library(pals)
library(patchwork)
library(highcharter)
library(dplyr)
library(GenomicRanges)
library(reactable)
library(data.table)
library(gridExtra)
library(ggpubr)
library(gprofiler2)
library(smplot)
```

```{r wd, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
setwd("~/Documents/hnscc_chipseq/nsd2oe")
wd <- paste0("~/Documents/hnscc_chipseq/nsd2oe")
```

# Cal27 NSD1KO-NSD2OE v PA

## Clusters
```{r cal27clus, echo=FALSE, fig.height=3, fig.width=8, message=FALSE, warning=FALSE}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.clus.fig.rda")
ps$Cal27
cell_line=paste0("Cal27")
control=paste0("PA")
test=paste0("NSD2OE")
mark=paste0("K36me2")
```

## Annotations - cluster A {.tabset}

### Ensembl regulatory build {.tabset .tabset-pills}

#### Genome-wide

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(sprintf("%s/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.enrich.rda",wd))
p1 <- ensembl.ol.plot.enrich
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.dep.rda")
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(sprintf("%s/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.enrich.igr.rda",wd))
p1 <- ensembl.ol.plot.enrich
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.dep.igr.rda")
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic
```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(sprintf("%s/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.enrich.g.rda",wd))
p1 <- ensembl.ol.plot.enrich
load("~/Documents/hnscc_chipseq/nsd2oe/plots/Cal27.PA.NSD2OE.K36me2.ensembl.ol.plot.dep.g.rda")
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

### ENCODE cCRE {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

### RepeatMasker {.tabset .tabset-pills}

#### Genome-wide

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic 
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

---

# SKN3-NSD2OE v PA

## Clusters
```{r echo = FALSE, warning=FALSE,message=FALSE,fig.width=8,fig.height=3}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/SKN3.P15.OE_NSD2.K36me2.clus.fig.rda")
ps$SKN3
cell_line=paste0("SKN3")
control=paste0("P15")
test=paste0("OE_NSD2")
mark=paste0("K36me2")
```

## Annotations - cluster A {.tabset}

### Ensembl regulatory build {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

### ENCODE cCRE {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic

```{r,echo = FALSE,fig.show = "hold", out.width = "50%", fig.align = "default"}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ccre.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ccre.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ccre.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ccre.ol.plot.dep
hw_grid(p1,p2)
```

### RepeatMasker {.tabset .tabset-pills}

#### Genome-wide

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic 
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.repeat.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- repeat.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.repeat.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- repeat.ol.plot.dep
hw_grid(p1,p2)
```

---

# SKN3-NSD2OE v SKN3-NSD1repair

## Clusters
```{r echo = FALSE, warning=FALSE,message=FALSE,fig.width=8,fig.height=3}
load("~/Documents/hnscc_chipseq/nsd2oe/plots/SKN3.NSD1repair.OE_NSD2.K36me2.clus.fig.rda")
ps$SKN3
cell_line=paste0("SKN3")
control=paste0("NSD1repair")
test=paste0("OE_NSD2")
mark=paste0("K36me2")
```

## Annotations - cluster A {.tabset}

### Ensembl regulatory build {.tabset .tabset-pills}

#### Genome-wide
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### IGR
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.igr.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.igr.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

#### Genic
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="50%",fig.align='center'}
load(file=sprintf("%s/plots/%s.%s.%s.%s.ensembl.ol.plot.enrich.g.rda",wd,cell_line,control,test,mark))
p1 <- ensembl.ol.plot.enrich
load(file=(sprintf('%s/plots/%s.%s.%s.%s.ensembl.ol.plot.dep.g.rda',wd,cell_line,control,test,mark)))
p2 <- ensembl.ol.plot.dep
hw_grid(p1,p2)
```

---

# FaDu-NSD2OE v PA

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
lfc <- fread("~/Documents/hnscc_chipseq/nsd2oe/data/mat.csv/FaDu.PA.OE_NSD2.K36me2.mat.csv")
smoothScatter(y = lfc$V1,x=lfc$V2,xlab = "PA",ylab="OE_NSD2")
```

---

# Cal27 RNAseq

```{r include = FALSE}
load("~/Documents/hnscc_chipseq/data/res.nsd1ko.c1.RData")
load("~/Documents/hnscc_chipseq/data/res.nsd1ko.c17.RData")
load("~/Documents/hnscc_chipseq/data/res.oe_nsd2.RData")
```

## Upregulated {.tabset}

### Relative to NSD1KO DEGs

Cutoff: Log2FC > 2 & normalized mean counts > 400
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
res.nsd1ko.c1.up <- res.nsd1ko.c1[res.nsd1ko.c1$baseMean>400,] %>%
  dplyr::filter(log2FoldChange > 2)
res.nsd1ko.c17.up <- res.nsd1ko.c17[res.nsd1ko.c17$baseMean>400,] %>%
  dplyr::filter(log2FoldChange > 2)
res.nsd1ko.c1.up$cond <- "NSD1KO.c1"
res.nsd1ko.c17.up$cond <- "NSD1KO.c17"
res.oe_nsd2$cond <- "OE_NSD2"
#
res.nsd1ko.oe_nsd2.up <- rbind(res.nsd1ko.c1.up,res.oe_nsd2[res.oe_nsd2$id %in% res.nsd1ko.c1.up$id,])
res.nsd1ko_c17.oe_nsd2.up <- rbind(res.nsd1ko.c17.up,res.oe_nsd2[res.oe_nsd2$id %in% res.nsd1ko.c17.up$id,])
#
p1 <- ggplot(data = res.nsd1ko.oe_nsd2.up,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
stat.p1 <- compare_means(log2FoldChange ~ cond, data = res.nsd1ko.oe_nsd2.up,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(11))
p1.final <- p1 + stat_pvalue_manual(stat.p1, label = "p.adj = {p.adj}")
#
#
p2 <- ggplot(data = res.nsd1ko_c17.oe_nsd2.up,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
#
stat.p2 <- compare_means(log2FoldChange ~ cond, data = res.nsd1ko_c17.oe_nsd2.up,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(11))
p2.final <- p2 + stat_pvalue_manual(stat.p2, label = "p.adj = {p.adj}")
#
grid.arrange(p1.final,p2.final,ncol=2)
```

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
tbl <- data.frame(samp = c("NSD1KO_C1","NSD1KO_C17"),total_DEG=c("308","123"),less_up = c(302,115))
reactable(tbl)
```

### Relative to NSD2OE DEGs

Cutoff: Log2FC > 1 & normalized mean counts > 400
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
res.oe_nsd2.up <- res.oe_nsd2[res.oe_nsd2$baseMean>400,] %>%
  dplyr::filter(log2FoldChange > 1)
#
res.nsd1ko.c1$cond <- "NSD1KO.c1"
res.nsd1ko.c17$cond <- "NSD1KO.c17"
#
res.oe_nsd2.nsd1ko_c1.up <- rbind(res.oe_nsd2.up,res.nsd1ko.c1[res.nsd1ko.c1$id %in% res.oe_nsd2.up$id,])
res.oe_nsd2.nsd1ko_c17.up <- rbind(res.oe_nsd2.up,res.nsd1ko.c17[res.nsd1ko.c17$id %in% res.oe_nsd2.up$id,])
#
p1 <- ggplot(data = res.oe_nsd2.nsd1ko_c1.up,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
stat.p1 <- compare_means(log2FoldChange ~ cond, data = res.oe_nsd2.nsd1ko_c1.up,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(11))
p1.final <- p1 + stat_pvalue_manual(stat.p1, label = "p.adj = {p.adj}")
#
#
p2 <- ggplot(data = res.oe_nsd2.nsd1ko_c17.up,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
#
stat.p2 <- compare_means(log2FoldChange ~ cond, data = res.oe_nsd2.nsd1ko_c17.up,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(11))
p2.final <- p2 + stat_pvalue_manual(stat.p2, label = "p.adj = {p.adj}")
#
grid.arrange(p1.final,p2.final,ncol=2)
```

less upregulated here means lower gene expression changes in NSD1KO compared to NSD2OE (about 60% of DEGs)
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
tbl <- data.frame(samp = c("NSD1KO_C1","NSD1KO_C17"),total_DEG=c("296","296"),less_up = c(179,185))
reactable(tbl)
```

---

## Downregulated {.tabset}

### Relative to NSD1KO DEGs

Cutoff: Log2FC < -2 & normalized mean counts > 400
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
res.nsd1ko.c1.down <- res.nsd1ko.c1[res.nsd1ko.c1$baseMean>400,] %>%
  dplyr::filter(log2FoldChange < -2)
res.nsd1ko.c17.down <- res.nsd1ko.c17[res.nsd1ko.c17$baseMean>400,] %>%
  dplyr::filter(log2FoldChange < -2)
#
res.nsd1ko.c1.down$cond <- "NSD1KO.c1"
res.nsd1ko.c17.down$cond <- "NSD1KO.c17"
#
res.nsd1ko.oe_nsd2.down <- rbind(res.nsd1ko.c1.down,res.oe_nsd2[res.oe_nsd2$id %in% res.nsd1ko.c1.down$id,])
res.nsd1ko_c17.oe_nsd2.down <- rbind(res.nsd1ko.c17.down,res.oe_nsd2[res.oe_nsd2$id %in% res.nsd1ko.c17.down$id,])
#
p1 <- ggplot(data = res.nsd1ko.oe_nsd2.down,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
#
stat.p1 <- compare_means(log2FoldChange ~ cond, data = res.nsd1ko.oe_nsd2.down,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(5))
p1.final <- p1 + stat_pvalue_manual(stat.p1, label = "p.adj = {p.adj}")
#
p2 <- ggplot(data = res.nsd1ko_c17.oe_nsd2.down,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
stat.p2 <- compare_means(log2FoldChange ~ cond, data = res.nsd1ko_c17.oe_nsd2.down,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(5))
p2.final <- p2 + stat_pvalue_manual(stat.p2, label = "p.adj = {p.adj}")
#
grid.arrange(p1.final,p2.final,ncol=2)
```

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
tbl <- data.frame(samp = c("NSD1KO_C1","NSD1KO_C17"),total_DEG=c("233","212"),less_down = c(232,210))
reactable(tbl)
```

### Relative to NSD2OE DEGs

Cutoff: Log2FC < -1 & normalized mean counts > 400
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
res.oe_nsd2.down <- res.oe_nsd2[res.oe_nsd2$baseMean>400,] %>%
  dplyr::filter(log2FoldChange < -1)
#
#
res.oe_nsd2.nsd1ko_c1.down <- rbind(res.oe_nsd2.down,res.nsd1ko.c1[res.nsd1ko.c1$id %in% res.oe_nsd2.down$id,])
res.oe_nsd2.nsd1ko_c17.down <- rbind(res.oe_nsd2.down,res.nsd1ko.c17[res.nsd1ko.c17$id %in% res.oe_nsd2.down$id,])
#
p1 <- ggplot(data = res.oe_nsd2.nsd1ko_c1.down,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
stat.p1 <- compare_means(log2FoldChange ~ cond, data = res.oe_nsd2.nsd1ko_c1.down,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(5))
p1.final <- p1 + stat_pvalue_manual(stat.p1, label = "p.adj = {p.adj}")
#
#
p2 <- ggplot(data = res.oe_nsd2.nsd1ko_c17.down,aes(x = cond, y = log2FoldChange)) +
  geom_violin(aes(fill = cond),show.legend = FALSE) +
  geom_boxplot(width=0.1, color="grey", alpha=2) +
  geom_line(aes(group = id),color="gray",alpha=0.3,size = 0.3) +
  geom_point(alpha=0.1) +
  xlab("") + 
  theme_bw()
#
stat.p2 <- compare_means(log2FoldChange ~ cond, data = res.oe_nsd2.nsd1ko_c17.down,paired = TRUE,p.adjust.method = "fdr", method = 'wilcox.test') %>% dplyr::select(-".y.") %>%
  mutate(y.position = c(5))
p2.final <- p2 + stat_pvalue_manual(stat.p2, label = "p.adj = {p.adj}")
#
grid.arrange(p1.final,p2.final,ncol=2)
```

less downregulated here means higher gene expression changes in NSD1KO compared to NSD2OE (about 35% of DEGs)
```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.show="hold", out.width="100%",fig.align='center'}
tbl <- data.frame(samp = c("NSD1KO_C1","NSD1KO_C17"),total_DEG=c("192","192"),less_down = c(71,62))
reactable(tbl)
```
